Documentation of Scripts for Generating Random MISDP Instances

### 2020-09-15 RIP-MISDP-Paper/scripts/RandomInstancesMISDP.tex
update documentation of RIP-CBF-formulation

  Output: Instances~\textsf{Matrices/type.m.n.k\_MISDP.side.pd.rank.socp.strgbnds[.nb]}, where

@@

  \item ``side''          : ``l'' (left side/$\alpha_k$), ``r'' (right side/$\beta_k$)

@@

  \item ``nobnds'' : ``nb'' (without stronger bounds~$-\tfrac{1}{2}z_j \leq X_{ij} \leq
\tfrac{1}{2}z_j$ for $i \neq j$), else nothing is added to the filename.

@@

  \item ``side'', ``Rank'', ``socp'', ``strgbnds'', ``nobnds'': see Output

@@

MIN (if ``side'' = l) \; or \; MAX (if ``side'' = r) \\

@@

\# cons: $2n^2+n+2 \quad {\color{blue}(n^2+n+2)}$, \qquad
\# cones = $5 \quad {\color{blue} (4)}$\\

@@

    &\text{L-} &n^2 \qquad & {\color{blue}-z_i - X_{ij} \leq 0},\quad & 0
    \leq i,\, j \leq n-1 &\qquad {\color{blue} \text{(this line is cancelled)}}\\
    &\text{L+} &n^2 \qquad & z_i - X_{ij} \geq 0,\quad & 0
    \leq i, \, j \leq n-1 \\
    &\text{L=}  &1 \qquad & \tr(X) - 1 = 0 \\

@@

\# entries: $4n^2+3n \quad {\color{blue} (- 2n^2)}$ \\

@@

@@

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDCONRANK1} is added.
\item If nobnds = 1: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} for VAR, CON. Additionally, the two
  lines in ACOORD with a \textcolor{blue}{blue constraint} are cancelled
  as well.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDCON, HCOORD, DCOORD in
  \textcolor{red}{red}. These inequalities are SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else.
\end{itemize}

@@

\# cons: $2n^2+n+2 \quad {\color{red}(+\tfrac{1}{2}n(n+3)(n+2))} \quad
{\color{blue} (-\tfrac{1}{2}n(n-1))}$, \qquad

@@

@@

    &\text{L-} &n^2\quad {\color{blue}(\tfrac{1}{2}n(n+1))} \qquad & -z_i - X_{ij} \leq 0,\;

@@

    \leq j \leq i \leq n-1)} \\
    &\text{L+} &n^2 \qquad & z_i - X_{ij} \geq 0,\quad & 0
    \leq j \leq i \leq n-1 \\
    &\text{L=}  &1 \qquad & \tr(X) - 1 = 0 \\

@@

\# entries: $2n^2+n$ \quad {\color{red} $+
  n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ } \quad {\color{blue} $- \tfrac{1}{2}n(n-1)$}\\

@@

to be added to the entries in the first column (scalar cons $i$).}

@@

\noindent
\textbf{ACOORD} (scalar cons $i$ | scalar var $j$ val) \\
\# entries: $2n^2+2n$ \qquad {\color{red} $(+2n)$} \qquad {\color{blue}
  $(-n^2)$} \\
\[
  \begin{aligned}
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + n+1} \quad & {\color{red}i} \quad &
    {\color{red}-\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle - \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + 2n+2} \quad & {\color{red}i} \quad &
    {\color{red}\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle + \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}
\[
  \begin{aligned}
    &i \quad & i \quad & -1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0, \dots,
    n-1 \\
    &n+in+j \quad & i \quad & -1.0\, (i =
    j),\; {\color{orange} -\tfrac{1}{2},\,(i \neq j)} \quad & {\color{blue}-z_i - X_{ij}
    \leq 0} \quad & 0 \leq i,\, j \leq n-1 \quad {\color{blue}
    (\text{this line is cancelled})} \\
    &n+n^2+in+j \quad & i \quad & 1.0\, (i =
    j),\; {\color{orange} \tfrac{1}{2},\,(i \neq j)}\quad & z_i - X_{ij}
    \geq 0 \quad & 0 \leq i,\, j \leq n-1 \\
    &n+2n^2+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \leq 0 \quad &
    i = 0,\dots,n-1 \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the third and fourth line.\\
}

\textbf{BCOORD} (scalar cons $i$ | val) \\
\# entries: $n+2 \qquad {\color{red} (+n(n+1))}$ \\
\[
\begin{aligned}
  &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + j} \quad & {\color{red}-1.0}
  \quad & {\color{red} \langle P_i, E_{j+1,j+1} \rangle - 1 = 0} \quad & {\color{red} j
  = 0,\dots,n,\; i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}
\[
  \begin{aligned}
    &i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    &2n^2+n \quad & -1.0 \quad & \tr(X) -1 = 0 \quad & \\
    &2n^2+n+1 \quad & k \quad & \sum z_i - k \leq 0 \quad & \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the second and third line.\\
}
}

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDVARRANK1} is added.
\item If nobnds = 1: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} in ACOORD.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDVAR, CON, FCOORD,
  ACOORD and BCOORD in \textcolor{red}{red}. These inequalities are
  SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else.
\end{itemize}

>>>>

  Output: Instances~\textsf{Matrices/type.m.n.k\_MISDP.side.pd.rank.socp.strgbnds.trineq.boundver}, where

@@

  \item ``side''          : ``$\ell$'' (left side/$\alpha_k$), ``r'' (right side/$\beta_k$)

@@

  \item ``trineq''        : 1 (add the trace constraint as inequality
    constraint, that is $\tr(X) \leq 1$ for right side, resp. $\tr(X) \geq
    1$ for th left side), 0 (use $\tr(X) == 1$ for both sides)
  \item  ``boundver''      :
    \item 0: $-z_i \leq X_{ii} \leq z_i,\; i \in [n]$, 
    \item 1: $-z_j \leq X_{ij} \leq z_j,\; i,j \in [n]$,
    \item 2: as 1 plus strengthened off-diagonal bounds
      $-0.5z_j \leq X_{ij} \leq 0.5z_j$ for $i \neq j$.

@@

  \item ``side'', ``Rank'', ``socp'', ``strgbnds'', ``trineq'', ``boundver'': see Output

@@

MIN (if ``side'' = $\ell$) \; or \; MAX (if ``side'' = r) \\

@@

\# cons: $2n^2+n+2 - {\color{blue}\text{strgbnds}\cdot n^2}$, \qquad
\# cones = $5 - {\color{blue} \text{strgbnds}}$\\
{\color{violet} If ``boundver'' = 0 : \# cons: $3n+2 - \text{strgbnds}\cdot n$} \\

@@

    &\text{L+} &n\; {\color{violet}(n)} \qquad & -z_i + 1 \geq 0, \quad & i = 0,\dots,n-1 \\
    &\text{L-} &n^2\; {\color{violet}(n)} \qquad & {\color{blue}-z_i - X_{ij} \leq 0},\quad & 0
    \leq i,\, j \leq n-1 &\qquad {\color{blue} \text{(this line is
        cancelled)}} \qquad {\color{violet} (\text{only for } i = j)}\\
    &\text{L+} &n^2\; {\color{violet}(n)} \qquad & z_i - X_{ij} \geq 0,\quad & 0
    \leq i, \, j \leq n-1 &\qquad {\color{violet} (\text{only for } i = j)}\\
    &\text{L=}  &1\; {\color{violet}(1)} \qquad & \tr(X) - 1 = 0 \quad & \qquad & \qquad
    {\color{cyan} \text{L}+ (\text{if ``side''} = \ell),\; \text{L}-
      (\text{if ``side'' = r})} \\
    &\text{L-}  &1\; {\color{violet}(1)} \qquad & \sum z_i - k \leq 0

@@

\# entries: $4n^2+3n - {\color{blue} \text{strgbnds}\cdot 2n^2}$ \\
{\color{violet} If ``boundver'' = 0 : \# entries: $7n -
  \text{strgbnds}\cdot 2n$. In this case, all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.} \\

@@

{\color{violet} If ``boundver'' = 0 : then all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.} \\

@@

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDCONRANK1} is added.
\item If trineq = 1: In CON the definition of the cone for the trace
  constraint is changed from~$\text{L}=$ to~\textcolor{cyan}{$\text{L-}$}
  or~\textcolor{cyan}{$\text{L}+$}, respectively.
\item If boundver = 0: The coupling constraints are only added for~$i = j$,
  i.e., {\color{violet} $-z_i \leq X_{ii} \leq z_i$, $i \in [n]$}. This
  changes the number of constraints in CON, and the number of entries in
  ACOORD, since all entries with $i \neq j$ in ACOORD need to be
  cancelled. Additionally, the first column (scalar cons $i$) in ACOORD and
  BCOORD needs to be adapted. See the changes in
  \textcolor{violet}{violet}.
\item If boundver = 2: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} for VAR, CON. Additionally, the two
  lines in ACOORD with a \textcolor{blue}{blue constraint} are cancelled
  as well.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDCON, HCOORD, DCOORD in
  \textcolor{red}{red}. These inequalities are SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else.
\end{itemize}

@@

\# cons: $2n^2+n+2 + {\color{red}\text{socp}\cdot(\tfrac{1}{2}n(n+3)(n+2))} - {\color{blue}
    \text{strgbnds} \cdot (\tfrac{1}{2}n(n-1))}$, \qquad

@@

{\color{violet} If ``boundver'' = 0: \# cons: $3n+2 +
  \text{socp}\cdot(\tfrac{1}{2}n(n+3)(n+2))$} \\

@@

    &\text{L-} &n^2\; {\color{blue}(\tfrac{1}{2}n(n+1))}\; {\color{violet}(n)} \qquad & -z_i - X_{ij} \leq 0,\;

@@

    \leq j \leq i \leq n-1)}\quad {\color{violet} (\text{only for } i=j)} \\
    &\text{L+} &n^2\; {\color{violet}(n)} \qquad & z_i - X_{ij} \geq 0,\quad & 0
    \leq j \leq i \leq n-1 \quad {\color{violet} (\text{only for } i=j)} \\
    &\text{L=}  &1 \qquad & \tr(X) - 1 = 0 \quad & \qquad
    {\color{cyan} \text{L+ (if ``side''} = \ell),\; \text{L- (if ``side'' = r})} \\

@@

\# entries: $2n^2+n$ + {\color{red} $\text{socp} \cdot
  n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ } - {\color{blue} $\text{strgbnds} \cdot
  \tfrac{1}{2}n(n-1)$}\\
{\color{violet} If ``boundver'' = 0: \# entries: $3n + \text{socp} \cdot
  n\cdot(3n+5+\tfrac{1}{2}n(n+1)) - \text{strgbnds} \cdot
  \tfrac{1}{2}n(n-1)$.}\\

@@

  to be added to the entries in the first column (scalar cons $i$).}\\
{\color{violet} If ``boundver = 0'', then all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.}\\

@@

\noindent
\textbf{ACOORD} (scalar cons $i$ | scalar var $j$ val) \\
\# entries: $2n^2+2n$ + {\color{red} $\text{socp}\cdot 2n$} - {\color{blue}
  $\text{strgbnds} \cdot n^2$} \\
{\color{violet} If ``boundver'' = 0: \# entries: $4n +\text{socp}\cdot 2n
  - \text{strgbnds} \cdot n$} \\
\[
  \begin{aligned}
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + n+1} \quad & {\color{red}i} \quad &
    {\color{red}-\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle - \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + 2n+2} \quad & {\color{red}i} \quad &
    {\color{red}\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle + \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}\\
{\color{violet} If ``boundver = 0'', then all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.}\\
\[
  \begin{aligned}
    &i \quad & i \quad & -1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0, \dots,
    n-1 \\
    &n+in+j \quad & i \quad & -1.0\, (i =
    j),\; {\color{orange} -\tfrac{1}{2},\,(i \neq j)} \quad & {\color{blue}-z_i - X_{ij}
    \leq 0} \quad & 0 \leq i,\, j \leq n-1 \quad {\color{blue}
    (\text{this line is cancelled})} \\
    &n+n^2+in+j \quad & i \quad & 1.0\, (i =
    j),\; {\color{orange} \tfrac{1}{2},\,(i \neq j)}\quad & z_i - X_{ij}
    \geq 0 \quad & 0 \leq i,\, j \leq n-1 \\
    &n+2n^2+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \leq 0 \quad &
    i = 0,\dots,n-1 \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the third and fourth line.\\
}

\textbf{BCOORD} (scalar cons $i$ | val) \\
\# entries: $n+2 \qquad {\color{red} (+n(n+1))}$ \\
\[
\begin{aligned}
  &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + j} \quad & {\color{red}-1.0}
  \quad & {\color{red} \langle P_i, E_{j+1,j+1} \rangle - 1 = 0} \quad & {\color{red} j
  = 0,\dots,n,\; i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}\\
{\color{violet} If ``boundver = 0'', then all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.}\\
\[
  \begin{aligned}
    &i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    &2n^2+n \quad & -1.0 \quad & \tr(X) -1 = 0 \quad & \\
    &2n^2+n+1 \quad & k \quad & \sum z_i - k \leq 0 \quad & \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the second and third line.\\
}
}

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDVARRANK1} is added.
\item If trineq = 1: In CON the definition of the cone for the trace
  constraint is changed from~$\text{L}=$ to~\textcolor{cyan}{$\text{L-}$}
  or~\textcolor{cyan}{$\text{L}+$}, respectively.
\item If boundver = 0: The coupling constraints are only added for~$i = j$,
  i.e., {\color{violet} $-z_i \leq X_{ii} \leq z_i$, $i \in [n]$}. This
  changes the number of constraints in CON, and the number of entries in
  FCOORD and ACOORD, since all entries with $i \neq j$ in FCOORD and ACOORD
  need to be cancelled. Additionally, the first column (scalar cons $i$) in
  FCOORD, ACOORD and BCOORD needs to be adapted. See the changes in
  \textcolor{violet}{violet}.
\item If boundver = 2: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} in ACOORD.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDVAR, CON, FCOORD,
  ACOORD and BCOORD in \textcolor{red}{red}. These inequalities are
  SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else.
\end{itemize}
